A space-time \skewt model for threshold exceedances

### 2016-06-29 LaTeX/response.tex

  \item In page 12, line -1: you mention the partition label switching problem appearing during the MCMC. This was not consequential for the inference? Can you expand on this? \\

  \begin{response}
    In a spatial analysis, the primary objectives are to make spatial predictions and to estimate extreme probabilities.
    Both of these objectives are met by marginalizing over partition-specific parameters and are thus unaffected by label switching.
    We have added a comment to this effect in the \sref{sts:simdesign}.
  \end{response}

  \item There are several papers using skew distributions in the spatial context. You should refer to the most relevant ones in your related work section. \\

  \begin{response}
    We have added several references to the introduction.
  \end{response}

@@

    \item Second, you said: ``all $z(s)$ and $\sigma(s)$ for sites in the sub-region k are assigned common values $z(s)$ = $z_k$ and $\sigma(s)$ = $\sigma_k$''. I guess you mean that for all $s \in P_k$, with $k = 1, 2, \ldots, K$, the functions $z(s)$ and $\sigma(s)$ are equal to the constants $z_k$ and $\sigma_k$, respectively. \\

    \begin{response}
      Yes, we now use your phrasing.
    \end{response}

    \item Finally, from the process definition in (6) $Y(s)$, the partitions in (7) and the elicitation of the random function in (8), why should we come to the conclusion that for locations that belong to different partitions, e.g. $s_i \in P_k$ and $s_j \in P_l$ with $P_k \neq P_l$, their distribution is not skew-$t$ anymore? You have only specified that within the same partition the distribution is skew-$t$, but what happens in the contrary case? In addition, from (9) it seems that for locations that belong to different partitions the distribution of the process is Gaussian. Is this correct? A clear explanation of this part is needed, adding the required steps. \\

    \begin{response}
      Setting aside the skewness parameter, the joint distribution of observations in different partition sets is that of $Y_1 = \sigma_1 e_1$ and $Y_2 = \sigma_2 e_2$ where $\sigma_1^2$ and $\sigma_2^2$ are independent inverse gamma and $(e_1, e_2)$ is bivariate normal.
      If $\sigma_1$ and $\sigma_2$ are fixed, then $(Y_1, Y_2)$ is bivariate normal, and if $\sigma_1 = \sigma_2$ is random then $(Y_1, Y_2)$ is bivariate $t$ marginal over $\sigma_1$.
      However, if $\sigma_1$ and $\sigma_2$ are different and unknown, then $\bY$ is neither Gaussian nor $t$.
      From our perspective (as we now mention above \eref{steq:chiskewt}), however, the important feature of this distribution is that it has asymptotic independence, which is sufficient to break the long-range dependence of the usual spatial-$t$ process.
    \end{response}

@@

  \item Page 11, Section 5, 8 lines from the bottom. You wrote ``the $v_t(s)$ terms were generated using\ldots ''. This is incorrect, $v_t(s)$ is not an observation. According to (10), $v_t(s)$ is a stochastic process. \\

  \begin{response}
    Yes, $v_t(\bs)$ is a stochastic process, and simulating data from the model requires generating $v$ at the data points from a multivariate normal distribution.
  \end{response}

  \item Appendix C, you use $\mu(\cdot)$ to denote the intensity measure of the Poisson point process but then $\mu$ is also a constant in the definition of the intensity measure. You should use different symbols. \\

  \begin{response}
    We now say throughout the proof in \aref{sta:proofsamepartition} that the point process is a homogeneous Poisson process with intensity $\lambda_{PP}$.
  \end{response}
\end{enumerate}

### 2016-06-29 LaTeX/skewt_rev.tex
updates to manuscript for revision

We propose a new spatiotemporal threshold exceedance model based on the \skewt process \citep{Padoan2011}.
\hl{Need to add in more references here to skew-$t$ used in a spatial setting.}
We use a \skewt distribution because of its flexibility to model asymmetry and heavy-tailed data with the aim of predicting the probability of exceeding a high fixed level at an unobserved location.
Our model allows for inference and predictions using the full likelihood with computing on the order of Gaussian models.
This allows us to use Bayesian methods, which we use to fit the model, handle censored data below the threshold, and make predictions at unobserved locations.
In a spatial setting, the multivariate \skewt distribution demonstrates asymptotic dependence between observations at all sites regardless of the distance between the sites.
In order to address this concern, we introduce a random spatial partition similar to the method used by \citet{Kim2005} for non-stationary Gaussian data.
This partitioning alleviates the asymptotic spatial dependence present in the \skewt distribution for sites that are far apart.

@@

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^\top$, and the covariate matrix $\bX_{n \times p} = [\bX(\bs_1), \ldots, \bX(\bs_n)]^\top$.
After marginalizing over both $z$ and $\sigma$, using the notation from \citet[p. 176]{Azzalini2014},
\begin{align} \label{steq:stazzalini}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, a),
\end{align}
that is, $\bY$ follows an $n$-dimensional \skewt distribution with location $\bX \bbeta \in \calR^n$; covariance matrix $\bOmega_{n \times n} = \bomega \bar{\bOmega} \bomega$ where \mbox{$\bar{\bOmega}_{n \times n} = \frac{1}{1 + \lambda^2}(\bSigma + \lambda^2 \bOne \bOne^\top)$}, $\bSigma_{n \times n}$ is the positive definite correlation matrix which is obtained from $\rho(h)$, and $\bomega_{n \times n} = \text{diag}\left(\sqrt{\frac{ b }{a(1 + \lambda^2)}}, \ldots, \sqrt{\frac{ b }{a(1 + \lambda^2)}} \right)$; slant parameters $\balpha \in \calR^n = \lambda (1 + \lambda^2)^{1 / 2} (1 + \lambda^2 \bOne^\top \bSigma^{-1} \bOne)^{-1/2} \bSigma^{-1} \bOne$, and degrees of freedom $a$.
Furthermore, the marginal distributions at each location also follow a univariate \skewt distribution \citep{Azzalini2014}.
This process is desirable because of its flexible tail that is controlled by the skewness parameter and degrees of freedom.
One major difference between the parameterization given in \eref{steq:fullmodel} and other parameterizations is that we characterize the skewnewss using $\lambda$ instead of the slant parameters $\balpha$.
For a more complete comparison with other parameterizations, see \aref{sta:otherparams}.

@@

The partitioning model removes long-range dependence. Conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs_1$ and $\bs_2$ in partitions $k_1$ and $k_2$ respectively is
\begin{align}
  \chi(h) &= I(k_1 = k_2) \chi_{\text{skew-}t}(h) \label{steq:chiskewt}
\end{align}
where $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a \skewt process given in equation \eref{steq:chiskew-t} of \aref{sta:skewt}, and $h = ||\bs_1 - \bs_2||$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_1 = k_2)$ is the probability that two sites separated by distance $h$ are in the same partition.
In \aref{sta:proofsamepartition}, we show that $\lim_{h \rightarrow \infty} \pi(h) = 0$, assuming that the knots follow a homogeneous Poisson process.
This implies that $\lim_{h \rightarrow \infty} \chi(h) = 0$.
In practice we fix $K$ at a finite value and use a uniform distribution for the knots $\bw_1, \ldots, \bw_K$.
In \fref{stfig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a \skewt distribution with $\alpha = 10$, and 3 degrees of freedom.
In \fref{stfig:chi} we estimate $\pi(h)$ through simulation.
% To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
% We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
% For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
% This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.

@@

\subsection{Computation}\label{sts:comp}
We use MCMC methods to explore the posterior.
At each MCMC iteration, we first impute values below the threshold conditional on observations above the threshold.
This is feasible for large datasets with our model because for a single day, conditional on the model parameters, we only need to draw from a truncated multivariate normal distribution.
We can use Gibbs sampling to update $Y_t(\bs)$ for censored observations that are below the threshold $T$.
After conditioning on $\lambda$, $z_t(\bs)$ and non-censored observations, $Y_t(\bs)$ has truncated normal full conditionals.
So we sample $Y_t(\bs) \sim N_{(-\infty, T)}(\bX_t^\top(\bs) \beta + \lambda | z_t(\bs)|, \bSigma)$.

Then, we update model parameters, $\Theta$, using a Metropolis-Hastings algorithm with Gibbs sampling when needed.
The final step of the computation is to use Bayesian Kriging to generate a predictive distribution for $Y_t(\bs^*)$ at prediction location $\bs^*$.
This step is similar to the imputation for censored observations except that the full conditionals are no longer truncated at $T$.
See Appendices A.1 and A.2 for details regarding the MCMC algorithm.

@@

\subsection{Design}\label{sts:simdesign}
For all simulation designs, we generated data from model \eref{steq:partition} in \sref{sts:part} using $n_s=144$ sites and $n_t=50$ independent days.
The sites were generated Uniform$([0, 10] \times [0, 10])$.
We generated data from 5 different simulation designs:
\begin{enumerate}[leftmargin=3em]
  \item Gaussian marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=5$ knots
  \item \Skewt marginal, $K=1$ knots
  \item \Skewt marginal, $K=5$ knots
  \item Max-stable with GEV(1, 1, 0.2) marginals \citep{Reich2012}
  % \item Transformation below $T = q(0.80)$
  \item A Brown-Resnick process with range 1 and smoothness 0.5
\end{enumerate}
In the first three designs, the $v_t(\bs)$ terms were generated using a \Matern covariance with smoothness parameter $\nu = 0.5$ and spatial range $\varphi = 1$.
For the covariance matrices in designs 1 -- 3, the proportion of the variance accounted for by the spatial variation was $\gamma = 0.9$ while the proportion of the variance accounted for by the nugget effect was $0.1$.
In the first design, $\sigma^2 = 2$ was used for all days which results in a Gaussian distribution.
For designs 2 and 3, $\sigma^2_{tk} \iid \text{IG}(3, 8)$ to give a $t$ distribution with 6 degrees of freedom.
For design 1, we set $\lambda = 0$.
For designs 2 and 3, $\lambda = 3$ was used as to simulate moderate skewness, and the $z_t$ were generated as described in Section \sref{sts:part}.
In designs 1 -- 3, the mean $\bX^\top \bbeta = 10$ was assumed to be constant across space.
In the fourth design, we generated from a spatial max-stable distribution \citep{Reich2012}.
In this design, data have marginal distributions that follow a generalized extreme value distribution with location parameter $1$, scale parameter $1$, and shape parameter $0.2$.
In this model, a random effect was used to induce spatial dependence using 144 spatial knots on a regular lattice in the square $[1, 9] \times [1, 9]$.
For this setting, $\gamma_{\text{RS}} \in (0, 1)$, is similar to $\gamma$ in that it controls the relative strength of the nugget effect.
We set $\gamma_{\text{RS}} = 0.5$, which represents moderate spatial dependence.
% In the final design, we generate $\tilde{y}$ using the setting from design 2, and then transform the data
% \begin{align}
%   y = \left\{ \begin{array}{lc}
%     \tilde{y}, \quad & \tilde{y} > T \\[0.5em]
%     T \exp\{\tilde{y} - T\}, \quad & \tilde{y} \le T
%   \end{array}\right.
% \end{align}
% where $T = q(0.80)$ is the 80th sample quantile of the data.
% The final design is included to explore the importance of using a threshold exceedance model when the distribution for the bulk of the data is misspecified.

$M = 50$ data sets are generated for each design.
For each data set we fit the data using six models
\begin{enumerate}[leftmargin=3em]
  \item Gaussian marginal, $K=1$ knots
  \item \Skewt marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item \Skewt marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
  \item A max-stable model based on \citet{Reich2012} thresholded at $T = q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
All methods are fit using a fully-Bayesian approach that simultaneously estimates marginal and spatial dependence parameters.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$ although only the intercept is used in the data generation.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\varphi \sim \text{Unif}(15)$.
The skewness parameter has prior $\lambda \sim N(0, 20)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(a / 2, b / 2)$, where $a$ has a discrete uniform prior on a mesh from $0.2$ to $20$ with spacing of $0.1$ and $b$ has a Gamma$(0.1, 0.1)$ prior.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We tried also fitting the \skewt marginals for the thresholded models, but it is very challenging for the MCMC to properly identify the skewness parameter with a censored left tail.
Each chain of the MCMC ran for 20,000 iterations with a burn-in period of 10,000 iterations.
Although the goal of this simulation study is not to assess parameter estimation, for design (2) and method (2) where data are generated and fit with a \skewt distribution, the sample converges for $\lambda$ and $a$, and the empirical coverage of posterior 95\% intervals is near the nominal level (96\% coverage for $\lambda$ and 90\% for $a$).
It should be noted that in the models with multiple partitions (i.e. models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC; however, we are not interested in these parameters but rather spatial predictions and tail probabilities which converge well.

@@

\subsection{Results}\label{sts:simresults}
We compared the Brier scores for exceeding 4 different high levels for each dataset.
The levels used for the Brier scores are extreme quantiles from the simulated data for $L = q(0.90)$, $q(0.95)$, $q(0.98)$, $q(0.99)$.
\fref{stfig:simbrierscores} gives the Brier score relative to the Brier score for the Gaussian method calculated as
\begin{align}
  \text{BS}_{\text{rel}} = \frac{\text{BS}_{\text{method}}}{\text{BS}_{\text{Gaussian}}}.
\end{align}
We analyzed the results for the simulation study using a Friedman \citep{Hollander2014} test at $\alpha = 0.05$ to see if at least one method had a significantly different Brier score.
For Friedman tests that came back with a significant p-value, we conducted a Wilcoxon-Nemenyi-McDonald-Thompson \citep{Hollander2014} test to see which of the methods had different results.
The full results for the Wilcoxon-Nemenyi-McDonald-Thompson tests are given in \aref{sta:pdiffs}.

In general, we find that when the method to fit the data matches the data generation scheme, there is some improvement over other methods.
The results show that when the data are generated from a Gaussian process, our method performs comparably to a Gaussian approach.
In general, when the underlying process is not Gaussian, our method results in an improvement over both the max-stable and Gaussian methods.
We also see that the non-thresholded methods tend to outperform the thresholded methods, but this is not surprising given that in most cases, the data are generated directly from the model used in the method.
Finally, in the case where the data are generated using a Brown-Resnick process, we find that our method is competitive with using a max-stable model.
% Finally, for setting 5, although the thresholded version of the single-partition model tends to perform the best across all of the extreme quantiles, the difference between the thresholded and non-thresholded methods is no longer significant in the more extreme quantiles.
In summary, our method provides more flexibility for data that demonstrate some level of asymmetry or heavy tails, while still performing comparably to Gaussian methods when the data are symmetric and have light tails.

@@

\section{Data analysis}\label{sts:analysis}
We consider daily observations of maximum 8-hour ozone measurements for the 31 days of July 2005 at 1,089 Air Quality System (AQS) monitoring sites in the United States as the response (see \fref{stfig:ozone-10jul}).
For each site, we also have covariate information containing the estimated ozone from the Community Multi-scale Air Quality (CMAQ) modeling system.
Initially, we fit a linear regression with $\bX_t(\bs) = [1, \text{CMAQ}_t(\bs)]^\top$. % assuming a mean function of
% \begin{align}
%   \text{E}[Y_i(\bs)] = \beta_0 + \beta_1 \cdot \text{CMAQ}_t(\bs). \label{steq:datamean}
% \end{align}
\fref{stfig:ozone-qq} shows a Q-Q plot of the residuals compared to a \skewt distribution with 10 d.f. and $\alpha = 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{plots/qq-res.pdf}
  \caption{Q-Q plot of the residuals for a \skewt distribution with 10 d.f. and $\alpha = 1$ (right)}
  \label{stfig:ozone-qq}
\end{figure}

Standard exploratory data analysis techniques for extremal dependence are very challenging with only 31 days worth of data because it is difficult to estimate extreme quantiles at each site to obtain empirical estimates of $\chi$.
Despite the fact that there is only one month of data, we can get some sense of extremal dependence between sites by looking at joint occurrences of high sample quantiles.
For example, \fref{stfig:bivariateozone} suggests there is more agreement between sites that are close to one another than sites that are far from one another.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{plots/daily-quantiles-ozone.pdf}
  \caption{Daily quantiles for two monitoring locations near Columbus, OH (left) and daily quantiles for a monitoring location in Los Angeles, CA and Columbus, OH (right)}
  \label{stfig:bivariateozone}
\end{figure}
Another aspect that distinguishes our approach from more traditional extremes analyses, is how the threshold is selected.
In our example, a threshold of 75 ppb which corresponds to $q(92)$ for all observations, but marginally it represents anywhere from $q(0.06)$ to $q(1)$.

@@

\section*{Supplementary Materials}
Web Appendices A--E are available with this paper at the Biometrics website on Wiley Online Library. \vspace*{-8pt}

>>>>

We propose a new spatiotemporal threshold exceedance model based on the \skewt process \citep{Padoan2011}.
We use a \skewt distribution because of its flexibility to model asymmetry and heavy-tailed data with the aim of predicting the probability of exceeding a high fixed level at an unobserved location.
Our model allows for inference and predictions using the full likelihood with computing on the order of Gaussian models.
This allows us to use Bayesian methods, which we use to fit the model, handle censored data below the threshold, and make predictions at unobserved locations.
The multivariate skew normal distribution was introduced by \citet{Azzalini1996}, and this was extended to the multivariate \skewt by \citet{Branco2001}.
These skew-elliptical distributions have been used in the spatial setting \citep{Genton2004,Kim2004}.
\citet{Zhang2010} propose the skew-Gaussian process as a class of stationary processes that have skewed marginal distributions.
\citet{Padoan2011} examined the usage of skew-Gaussian and \skewt distributions for multivariate extremes.
In a spatial setting, the multivariate \skewt distribution demonstrates asymptotic dependence between observations at all sites regardless of the distance between the sites.
In order to address this concern, we introduce a random spatial partition similar to the method used by \citet{Kim2005} for non-stationary Gaussian data.
This partitioning alleviates the asymptotic spatial dependence present in the \skewt distribution for sites that are far apart.

@@

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^\top$, and the covariate matrix $\bX_{n \times p} = [\bX(\bs_1), \ldots, \bX(\bs_n)]^\top$.
After marginalizing over both $z$ and $\sigma$, using the notation from \citet[p. 176]{Azzalini2014},
\begin{align} \label{steq:stazzalini}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, a),
\end{align}
that is, $\bY$ follows an $n$-dimensional \skewt distribution with location $\bX \bbeta \in \calR^n$; covariance matrix $\bOmega_{n \times n} = \bomega \bar{\bOmega} \bomega$ where \mbox{$\bar{\bOmega}_{n \times n} = \frac{1}{1 + \lambda^2}(\bSigma + \lambda^2 \bOne \bOne^\top)$}, $\bSigma_{n \times n}$ is the positive definite correlation matrix which is obtained from $\rho(h)$, and $\bomega_{n \times n} = \text{diag}\left(\sqrt{\frac{ b }{a(1 + \lambda^2)}}, \ldots, \sqrt{\frac{ b }{a(1 + \lambda^2)}} \right)$; slant parameters $\balpha \in \calR^n = \lambda (1 + \lambda^2)^{1 / 2} (1 + \lambda^2 \bOne^\top \bSigma^{-1} \bOne)^{-1/2} \bSigma^{-1} \bOne$, and degrees of freedom $a$.
Furthermore, the marginal distributions at each location also follow a univariate \skewt distribution \citep{Azzalini2014}.
This process is desirable because of its flexible tail that is controlled by the skewness parameter and degrees of freedom.
% One major difference between the parameterization given in \eref{steq:fullmodel} and other parameterizations is that we characterize the skewnewss using $\lambda$ instead of the slant parameters $\balpha$.
For a comparison with other parameterizations, see \aref{sta:otherparams}.

@@

The partitioning model removes long-range dependence. Conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs_1$ and $\bs_2$ in partitions $k_1$ and $k_2$ respectively is
\begin{align}
  \chi(h) &= I(k_1 = k_2) \chi_{\text{skew-}t}(h) \label{steq:chiskewt}
\end{align}
where $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a \skewt process given in equation \eref{steq:chiskew-t} of \aref{sta:skewt}, and $h = ||\bs_1 - \bs_2||$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where \mbox{$\pi(h) = \Pr(k_1 = k_2)$} is the probability that two sites separated by distance $h$ are in the same partition.
In \aref{sta:proofsamepartition}, we show that $\lim_{h \rightarrow \infty} \pi(h) = 0$, assuming that the knots follow a homogeneous Poisson process.
This implies that $\lim_{h \rightarrow \infty} \chi(h) = 0$.
In practice we fix $K$ at a finite value and use a uniform distribution for the knots $\bw_1, \ldots, \bw_K$.
In \fref{stfig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a \skewt distribution with $\alpha = 10$, and 3 degrees of freedom.
In \fref{stfig:chi} we estimate $\pi(h)$ through simulation.
% To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
% We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
% For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
% This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.

@@

\subsection{Computation}\label{sts:comp}
We use MCMC methods to explore the posterior distribution of the model parameters.
At each MCMC iteration, we first impute values below the threshold conditional on observations above the threshold.
This is feasible for large datasets with our model because for a single day, conditional on the model parameters, we only need to draw from a truncated multivariate normal distribution.
We can use Gibbs sampling to update $Y_t(\bs)$ for censored observations that are below the threshold $T$.
After conditioning on $\lambda$, $z_t(\bs)$ and non-censored observations, $Y_t(\bs)$ has truncated normal full conditionals.
So we sample $Y_t(\bs) \sim N_{(-\infty, T)}(\bX_t^\top(\bs) \beta + \lambda | z_t(\bs)|, \bSigma)$.

We update model parameters $\Theta$ using Gibbs sampling with Metropolis-Hastings steps when needed.
In our case, we also wish to be able to make predictions at sites where we do not have data.
We can easily implement Bayesian Kriging as a part of the algorithm to generate a predictive distribution for $Y_t(\bs^*)$ at prediction location $\bs^*$.
This step is similar to the imputation for censored observations except that the full conditionals are no longer truncated at $T$.
See Appendices A.1 and A.2 for details regarding the MCMC algorithm.

@@

\subsection{Design}\label{sts:simdesign}
For all simulation designs, we generated data from model \eref{steq:partition} in \sref{sts:part} using $n_s=144$ sites and $n_t=50$ independent days.
The sites were generated uniformly on the square $[0, 10] \times [0, 10]$.
We generated data from five different simulation designs:
\begin{enumerate}[leftmargin=3em]
  \item Gaussian, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=1$ knot
  % \item Symmetric-$t$ marginal, $K=5$ knots
  \item \Skewt, $K=1$ knots
  \item \Skewt, $K=5$ knots
  \item Multivariate asymmetric logistic distribution \citep{Stephenson2003} %with GEV(1, 1, 0.2) marginals with dependence parameteter $\gamma_{\text{AL}} = 0.5$
  % \item Transformation below $T = q(0.80)$
  \item Brown-Resnick max-stable process \citep{Kabluchko2009} %with unit Fréchet marginals and stable semivariogram with range 1 and smoothness 0.5
\end{enumerate}
In the first three designs, the $v_t(\bs)$ terms were generated using a \Matern covariance with smoothness parameter $\nu = 0.5$ and spatial range $\varphi = 1$.
For the covariance matrices in designs 1 -- 3, the proportion of the variance accounted for by the spatial variation was $\gamma = 0.9$ while the proportion of the variance accounted for by the nugget effect was $0.1$.
In the first design, $\sigma^2 = 2$ was used for all days which results in a Gaussian distribution.
For designs 2 and 3, $\sigma^2_{tk} \iid \text{IG}(3, 8)$ to give a $t$ distribution with 6 degrees of freedom.
For design 1, we set $\lambda = 0$.
For designs 2 and 3, $\lambda = 3$ was used as to simulate moderate skewness, and the $z_t$ were generated as described in Section \sref{sts:part}.
In designs 1 -- 3, the mean $\bX^\top \bbeta = 10$ was assumed to be constant across space.
In the fourth design, we generated from a multivariate asymmetric logistic distribution \citep{Stephenson2003}.
In this design, data have marginal distributions that follow a generalized extreme value distribution with location parameter $1$, scale parameter $1$, and shape parameter $0.2$.
In this model, a random effect was used to induce spatial dependence using 144 spatial knots on a regular lattice in the square $[1, 9] \times [1, 9]$.
For this setting, we set the dependence parameter $\gamma_{\text{AL}} = 0.5$ which gives moderate spatial dependence.
For the asymmetry parameters, we use standardized Gaussian as in \citet{Reich2012} with bandwidth 1.
The dependence parameter $\gamma_{\text{AL}} \in (0, 1)$, is similar to $\gamma$ in that it controls the relative strength of the nugget effect.
For the final design, we generate data from a Brown-Resnick max-stable process \citep{Kabluchko2009} using \texttt{rmaxtab} in the \texttt{SpatialExtremes} package of \texttt{R} \citep{Ribatet2015}.
For this design we give choose unit \Frechet margins, and use a range of 1 with smoothness 0.5.
% In the final design, we generate $\tilde{y}$ using the setting from design 2, and then transform the data
% \begin{align}
%   y = \left\{ \begin{array}{lc}
%     \tilde{y}, \quad & \tilde{y} > T \\[0.5em]
%     T \exp\{\tilde{y} - T\}, \quad & \tilde{y} \le T
%   \end{array}\right.
% \end{align}
% where $T = q(0.80)$ is the 80th sample quantile of the data.
% The final design is included to explore the importance of using a threshold exceedance model when the distribution for the bulk of the data is misspecified.

$M = 50$ data sets are generated for each design.
For each data set we fit the data using six models
\begin{enumerate}[leftmargin=3em]
  \item Gaussian marginal, $K=1$ knots
  \item \Skewt marginal, $K=1$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=1$ knots, $T=q(0.80)$
  \item \Skewt marginal, $K=5$ knots, $T=-\infty$
  \item Symmetric-$t$ marginal, $K=5$ knots, $T=q(0.80)$
  \item A max-stable model based on \citet{Reich2012} thresholded at $T = q(0.80)$
\end{enumerate}
where $q(0.80)$ is the 80th sample quantile of the data.
All methods are fit using a fully-Bayesian approach that simultaneously estimates marginal and spatial dependence parameters.
The design matrix $\bX$ includes an intercept with a first-order spatial trend with priors of $\beta_\text{int}$, $\beta_\text{lat}$, $\beta_\text{long},  \iid \text{N}(0, 10)$ although only the intercept is used in the data generation.
The spatial covariance parameters have priors $\log(\nu) \sim \text{N}(-1.2, 1)$, $\gamma \sim \text{Unif}(0, 1)$, $\varphi \sim \text{Unif}(0, 15)$.
The skewness parameter has prior $\lambda \sim N(0, 20)$.
The residual variance terms have priors $\sigma^2_t(\bs) \sim \text{IG}(a / 2, b / 2)$, where $a$ has a discrete uniform prior on a mesh from $0.2$ to $20$ with spacing of $0.1$ and $b$ has a Gamma$(0.1, 0.1)$ prior.
The knots have priors $\bw \sim \text{Unif}(\calD)$.
We tried also fitting the \skewt marginals for the thresholded models, but it is very challenging for the MCMC to properly identify the skewness parameter with a censored left tail.
Each chain of the MCMC ran for 20,000 iterations with a burn-in period of 10,000 iterations.
Although the goal of this simulation study is not to assess parameter estimation, for design (2) and method (2) where data are generated and fit with a \skewt distribution, the samples converges for $\lambda$ and $a$, and the empirical coverage of posterior 95\% intervals is near the nominal level (96\% coverage for $\lambda$ and 90\% for $a$).
It should be noted that in the models with multiple partitions (i.e. models 4 and 5) it is hard to assess the convergence of $\bw$, $z(\bs)$, and $\sigma^2(\bs)$ because of partition label switching throughout the MCMC; however, we are not interested in these parameters but rather spatial predictions and tail probabilities which converge well.
Finally, we do not fit a Brown-Resnick model because we cannot use a Bayesian approach with so many sites.

@@

\subsection{Results}\label{sts:simresults}
We compared the Brier scores for exceeding four different high levels for each dataset.
The levels used for the Brier scores are extreme quantiles from the simulated data for $L = q(0.90)$, $q(0.95)$, $q(0.98)$, $q(0.99)$.
\fref{stfig:simbrierscores} gives the Brier score relative to the Brier score for the Gaussian method calculated as
\begin{align}
  \text{BS}_{\text{rel}} = \frac{\text{BS}_{\text{method}}}{\text{BS}_{\text{Gaussian}}}.
\end{align}
We analyzed the results for the simulation study using a Friedman \citep{Hollander2014} test at $\alpha = 0.05$ to see if at least one method had a significantly different Brier score.
For Friedman tests that came back with a significant p-value, we conducted a Wilcoxon-Nemenyi-McDonald-Thompson \citep{Hollander2014} test to see which of the methods had different results.
The full results for the Wilcoxon-Nemenyi-McDonald-Thompson tests are given in \aref{sta:pdiffs}.

In general, we find that when the method to fit the data matches the data generation scheme, there is some improvement over other methods.
The results show that when the data are generated from a Gaussian process, our method performs comparably to a Gaussian approach.
In general, when the underlying process is not Gaussian, our method results in an improvement over both the max-stable and Gaussian methods.
We also see that the non-thresholded methods tend to outperform the thresholded methods, but this is not surprising given that in most cases, the data are generated directly from the model.
Finally, in the case where the data are generated from a Brown-Resnick process, we find that our method is competitive with using a max-stable model.
% Finally, for setting 5, although the thresholded version of the single-partition model tends to perform the best across all of the extreme quantiles, the difference between the thresholded and non-thresholded methods is no longer significant in the more extreme quantiles.
In summary, our method provides great flexibility for data that demonstrate some level of asymmetry and heavy tails, while still performing comparably to Gaussian methods when the data are symmetric and have light tails.

@@

\section{Data analysis}\label{sts:analysis}
We consider daily observations of maximum 8-hour ozone measurements for the 31 days of July 2005 at 1,089 Air Quality System (AQS) monitoring sites in the United States as the response (see \fref{stfig:ozone-10jul}).
For each site, we also have covariate information containing the estimated ozone from the Community Multi-scale Air Quality (CMAQ) modeling system.
Initially, we fit a linear regression with $\bX_t(\bs) = [1, \text{CMAQ}_t(\bs)]^\top$. % assuming a mean function of
% \begin{align}
%   \text{E}[Y_i(\bs)] = \beta_0 + \beta_1 \cdot \text{CMAQ}_t(\bs). \label{steq:datamean}
% \end{align}
\fref{stfig:ozone-qq} shows a Q-Q plot of the residuals compared to a \skewt distribution with $a = 10$ and $\lambda = 1$.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{plots/qq-res.pdf}
  \caption{Gaussian Q-Q plot (left) and \skewt distribution with $a = 10$ and $\lambda = 1$ Q-Q plot (right) for of the residuals.}
  \label{stfig:ozone-qq}
\end{figure}

Standard exploratory data analysis techniques for extremal dependence are very challenging with only 31 days worth of data because it is difficult to estimate extreme quantiles at each site to obtain empirical estimates of $\chi$.
Despite the fact that there is only one month of data, we can get some sense of extremal dependence between sites by looking at joint occurrences of high sample quantiles.
For example, \fref{stfig:bivariateozone} suggests there is more agreement between sites that are close to one another than sites that are far from one another.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{plots/daily-quantiles-ozone.pdf}
  \caption{Daily quantiles for two monitoring locations near Columbus, OH (left) and daily quantiles for a monitoring location in Los Angeles, CA and Columbus, OH (right)}
  \label{stfig:bivariateozone}
\end{figure}
% Another aspect that distinguishes our approach from more traditional extremes analyses, is how the threshold is selected.
% In our example, a threshold of 75 ppb which corresponds to $q(92)$ for all observations, but marginally it represents anywhere from $q(0.06)$ to $q(1)$.

@@

\section*{Supplementary Materials}
Web Appendices A--E are available with this paper at the Biometrics website on Wiley Online Library.
\texttt{R} code implementing the spatial \skewt model for threshold exceedances is available with this paper at the Biometrics website on Wiley Online Library.\vspace*{-8pt}
